---
title: "Testing for Xiaohan's package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction
First off, thank you so much for downloading my package, and the name of it is
just my netid:xw547. To load the package, you may use:


```{r setup}
library(xw547)
```

As required by Professor Basu, there are three functions. Also, there are several
helper functions. To wit, you may use the command below to 
```{r}
??xw547
```
By clicking xw547::overview, you may find an overview of my functions. 

Then, we would proceed to the testing part of my package.

## solve_ols
As the name indicates, the function is an implementation of the Gauss-Seidel and 
the Jacobi method we metioned in class.

As always, you cal always check out the helper documentation by 
```{r}
?solve_ols
```

And we can do a simulation similar to what we have done in the HW1
```{r}
###Helper function that generates A in HW1
generate_A <- function(n, alpha){
  A <- diag(rep(alpha,n))
  for (i in 1:(n-1)){
    A[i+1, i] <- -1
    A[i, i+1] <- -1
  }
  return(A)
}

###generate data matrix and response
A_1 = generate_A(100,1)
A_2 =generate_A(100,2)
A_3 =generate_A(100,3)

v = rep(c(1,0),50)
b_1 = A_1%*%v
b_2 = A_2%*%v
b_3 = A_3%*%v

###A_1, and the both algorithm is diverged
# solve_ols(A_1,b_1)
# solve_ols(A_1, b_1, method = "Jacobi")

###A_3,
#Gauss-Seidel Method
solve_ols(A_3, b_3, method = "Gauss")
#Sequential Jacobi Method
solve_ols(A_3, b_3, method = "Jacobi")
#Parallel Jacobi
solve_ols(A_3, b_3, method = "Jacobi", parallel = TRUE)
```

The unsolvable linear system $A_1, b_1$ should return warning, and they are 
commented out in the code chunk. Also, we can give an output of the full result 
of each iteration. And each row should be the result from one of the iteration.

```{r}
solve_ols(A_3, b_3, method = "Gauss", full_result = TRUE)
```


## algo_leverage
Also, you can implement the method by 

