---
title: "Testing for Xiaohan's package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction
First off, thank you so much for downloading my package, and the name of it is
just my netid:xw547. To load the package, you may use:


```{r setup}
library(xw547)
```

As required by Professor Basu, there are three functions. Also, there are several
helper functions. To wit, you may use the command below to 
```{r}
??xw547
```
By clicking xw547::overview, you may find an overview of my functions. 

Then, we would proceed to the testing part of my package.

## solve_ols
As the name indicates, the function is an implementation of the Gauss-Seidel and 
the Jacobi method we metioned in class.

As always, you cal always check out the helper documentation by 
```{r}
?solve_ols
```

And we can do a simulation similar to what we have done in the HW1
```{r}
###Helper function that generates A in HW1
generate_A <- function(n, alpha){
  A <- diag(rep(alpha,n))
  for (i in 1:(n-1)){
    A[i+1, i] <- -1
    A[i, i+1] <- -1
  }
  return(A)
}

###generate data matrix and response
A_1 = generate_A(100,1)
A_2 =generate_A(100,2)
A_3 =generate_A(100,3)

v = rep(c(1,0),50)
b_1 = A_1%*%v
b_2 = A_2%*%v
b_3 = A_3%*%v


```









